Generating the Blueprints of Java Ecosystem

### 2015-02-22 msr.tex
a little work on related work

  \item \textbf{JDepend} \textit{(jdep)}~\cite{JDEPEND} is an source tool that analyses {\sc jar} files that contain compiled Java classes and calculates a series of design metrics.

@@

Figure~\ref{fig:database-schema} illustrates the database

@@

The initial goal of this experiment was simply to provide quantifiable results that are indicative regarding the usage of each {\sc dsl}, thus only files containing Java code were taken into account. Build files or other resources that may contain {\sc dsl}s were not included.

One final assumption was also made; if {\sc xpath} or {\sc xslt} were found in the source code, then the project would be marked that it also uses {\sc xml}, since those two languages are used for query and transformations on {\sc xml} {\sc dom} trees.

\begin{figure}
\centering
\includegraphics[scale=0.65]{dsl-usage}
\caption{DSL language usage in Java projects}
\label{fig:dsl-usage}
\end{figure}

@@

The Maven ecosystem has been previously analyzed by Raemaekers et al.~\cite{RDV13} to produce the {\it Maven dependency dataset}. Apart from basic information like individual methods, classes, packages and lines of code for every {\sc jar}, this dataset also includes a database with all the connections between the aforementioned elements. Our work differs from this research because it reports all bugs coming from the output of a static analysis tool, for each {\sc jar} contained in the Maven repository.

In publication \cite{MKLGS14}, a

>>>>

  \item \textbf{JDepend} \textit{(jdep)}~\cite{JDEPEND} is a tool that analyses {\sc jar} files that contain compiled Java classes and calculates a series of design metrics.

@@

Figure~\ref{fig:database-schema} illustrates the database schema. The data are stored in a straightforward manner.

@@

The initial goal of this experiment was simply to provide quantifiable results that are indicative regarding the usage of each {\sc dsl}, thus only files containing Java code were taken into account. Build files or other resources that may contain {\sc dsl}s were not included. One final assumption was also made; if {\sc xpath} or {\sc xslt} were found in the source code, then the project would be marked that it also uses {\sc xml}, since those two languages are used for query and transformations on {\sc xml} {\sc dom} trees.

@@

The Maven ecosystem has been previously analyzed by Raemaekers et al.~\cite{RDV13} to produce the {\it Maven dependency dataset}. Apart from basic information like individual methods, classes, packages and lines of code for every {\sc jar}, this dataset also includes a database with all the connections between the aforementioned elements. In publication \cite{MKLGS14}, Mitropoulos et al. also experimented in a similar way, by running the findbugs~\cite{HP04} security and bugs audit tool on a large part of the maven repository. Our work differs from these these two approaches since it presents the metrics calculated by the three aforementioned tools; \textit{ckjm}, \textit{jdepend}, and \textit{clmt}.
